Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-01-21 docs/papers/roofline_model/gocean_roofline.tex
roofline: add plot of STREAM2 results on desktop and table containing vital statistics

\begin{table}
\begin{tabular}{l|c|c|c|c}
  & \multicolumn{2}{c|}{E5-1620 v.~2, 3.7GHz} & \multicolumn{2}{c}{E5-2697 v.~2, 2.7GHz}  \\
  \hline
  L2 Cache (KB)             & \multicolumn{2}{c|}{256} &  \multicolumn{2}{c}{256}  \\
  L3 Cache (MB)             & \multicolumn{2}{c|}{10}  &  \multicolumn{2}{c}{30}  \\
  \hline
  Array size ($10^6$ words) &   0.25 &  5      &  0.25  & 0.5    & 15 \\
  STREAM, Triad (GB/s)      &  35.49 & 17.64   & 29.271 & 13.8426 & 9.6218 \\
  \hline
 LINPACK (GFLOPS)      & \multicolumn{2}{c|}{28.32}  & \multicolumn{2}{c}{25.41} \\
\hline
\end{tabular}
\caption{The STREAM and LINPACK benchmark results for a single thread
  running on each of the two CPUs considered here.}
\label{TAB_stream_linpack}
\end{table}

>>>>

Interpreting the results of the STREAM benchmark in order to get
bandwidth figures for all levels of the cache hierarchy is not
straightforward. We therefore used the STREAM2 benchmark which is
intended for this purpose. In Figure~\ref{FIG_stream2_desktop} we plot
the results obtained from the DAXPY component of the STREAM2 benchmark
on the E5-1620 CPU. The plateaux in bandwidth for L2, L3 and main
memory are clear but that for L1 is considerably noisier. The final
values we have used in the roofline plots are given in
Table~\ref{TAB_stream_linpack}.

\begin{figure}
\includegraphics{stream2_desktop}
\caption{Results from running the STREAM2 benchmark on the E5-1620 CPU.}
\label{FIG_stream2_desktop}
\end{figure}

\begin{table}
\begin{tabular}{|l|c|c|c|c|}
\hline
  \multicolumn{5}{|c|}{E5-1620 v.~2, 3.7GHz} \\
  \hline
LINPACK (GFLOPS) & \multicolumn{4}{c|}{28.32} \\
\hline
 &  L1 Cache & L2 Cache & L3 Cache & Main memory \\
 &   32 KB   & 256 KB   & 10 MB    &  --         \\
\hline
STREAM2 (GB/s)   &  117  &  65.8  & 46.7 &  20.5 \\
  \hline
\multicolumn{5}{|c|}{E5-2697 v.~2, 2.7GHz}  \\
\hline
LINPACK (GFLOPS) & \multicolumn{4}{c|}{25.41} \\
\hline
 & L1 Cache & L2 Cache & L3 Cache & Main memory \\
 &   32 KB  & 256 KB   & 30 MB    &  --         \\
\hline
STREAM2 (GB/s) &   &   &  &  \\
\hline
\end{tabular}
\caption{The STREAM and LINPACK benchmark results for a single thread
  running on each of the two CPUs considered here.}
\label{TAB_stream_linpack}
\end{table}
